A tool set for random number generation on GPUs in R

### 2021-12-07 pkg/gpuRandom/inst/documents/paper1_2021_5/paper1.Rnw
r functions
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/diseasemapping@3031 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

 <<monthdata,eval=TRUE,echo=FALSE, cache=TRUE, fig.pos='h', message=FALSE>>=
library(knitr)
library(tidyverse)
library(kableExtra)
knitr::kable(month,format="latex", align = c("rrrrrrrrrrrr"), #label="tab:month"
  caption = "Monthly birth anomaly data\\label{tab:month}", booktabs=TRUE,linesep = "") %>%
  kable_styling(full_width = F, position = "center")#latex_options = "HOLD_position")
@

>>>>

 <<monthdata,eval=TRUE,echo=FALSE, cache=TRUE, fig.pos='h', message=FALSE,purl=FALSE>>=
library(knitr)
library(tidyverse)
library(kableExtra)
knitr::kable(month,format="latex", align = c("rrrrrrrrrrrr"), #label="tab:month"
  caption = "Monthly birth anomaly data\\label{tab:month}", booktabs=TRUE,linesep = "") %>%
  kable_styling(full_width = F, position = "center")#latex_options = "HOLD_position")
@
<<monthDataForScript, include=FALSE, purl=TRUE>>-
knitr::kable(month)
@
